### 2016-05-24 intro.tex
intro hacking still

In particular, say that $\mathbf{B}_1$ is implementing a classic Bloom filter.  Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$B_1$.  Let's assume the former, for the moment.  In order for~$B_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.  Since~$B_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.  But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.  Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.  Morevover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations. Thus, if we assume that $\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their formalization fails to capture the basic Bloom filter construction; at best, it is hard to see clearly that it does.

@@

Later, we give syntax for ASM primitives that also admit operations upon the set representation.  This captures so-called counting Bloom filters that are used, for example, in fairness-enforcing algorithms for routing of TCP streams.  It also captures... \tsnote{finish}

We show that... \tsnote{finish}

>>>>

In particular, say that $\mathbf{B}_1$ is implementing a classic Bloom filter.  Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.  Let's assume the former, for the moment.  In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.  Since~$B_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.  But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.  Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.  Morevover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations. Thus, if we assume that $\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their formalization fails to capture the basic Bloom filter construction; at best, it is hard to see clearly that it does.

@@

Later, we give syntax for ASM primitives that also admit operations upon the set representation.  This captures so-called counting Bloom filters that are used, for example, in fairness-enforcing algorithms for routing of TCP streams.  It also captures...

We show that...

\heading{Related work. }

\tsnote{Stopped here.}
